Total Platform Cyber Protection

### 2016-06-11 paper.tex
Computing Stack layers diagram is added

@@

Modern computing infrastructure serves a wide array of needs, with
diverse technologies and implementations: embedded systems, cloud
computing, sensor networks, desktops, mobile devices, and industrial
control systems. Rather than consider each of these computing
platforms independently, in this work we abstracted the computing
platform into several layers, each of which are applicable to every
computing infrastructure. In particular, we analyzed the security
research performed at the following layers of the computing platform:
hardware, firmware, bus, hypervisor, operating system, application,
and network layers.

@@

In this report, we will first discuss the computing stack, and, for
every layer, we will describe the layer, identify primary threats
against the layer, and summarize the research on attempts to secure
that layer, and finally we will determine areas that require further
research investment to ensure the security of the layer.

>>>>

\usepackage{tikz}
\usetikzlibrary{positioning}
\definecolor{nodecolor}{RGB}{202,202,202}
\newlength\framesep
\setlength\framesep{16pt}
\pgfdeclarelayer{background}
\pgfsetlayers{background,main}
\pgfkeys{
	/tikz/node distance/.append code={
		\pgfkeyssetvalue{/tikz/node distance value}{#1}
	}
}

@@

Modern computing infrastructure serves a wide array of needs, with
diverse technologies and implementations: embedded systems, cloud
computing, sensor networks, desktops, mobile devices, and industrial
control systems. Rather than consider each of these computing
platforms independently, in this work we abstracted the computing
platform into several layers, each of which are applicable to every
computing infrastructure. In particular, we analyzed the security
research performed at the following layers of the computing platform:
hardware, firmware, bus, hypervisor, operating system, application,
and network layers (Figure~1).

@@

In this report, we will first discuss the computing stack, and, for
every layer, we will describe the layer, identify primary threats
against the layer, and summarize the research on attempts to secure
that layer, and finally we will determine areas that require further
research investment to ensure the security of the layer.\input{fig_layers}
